this is for the result part of the draft

### 2017-03-29 analysis/draft.Rmd
Files commited by wflow_commit.

@@

there is somethig we don't fully understand.

>>>>

```{r}
library(ggplot2)
movie_res = readRDS("../data/missingvalue/box_movies.rds")
tumor_res = readRDS("../data/missingvalue/box_tumor.rds")
president_res = readRDS("../data/missingvalue/box_president.rds")
breast_res = readRDS("../data/missingvalue/box_breast.rds")
gtex_res = readRDS("../data/missingvalue/box_gtex.rds")
plot_res = function(output,title = "data"){
  rmse = as.vector(output)
  N = dim(output)[1]
  methods = rep(c("flash","NBSFA","PMD","softImpute"), each = N)
  df = data.frame(RMSE = rmse, Method = methods )
  p<-ggplot(df, aes(x=Method, y=RMSE, color=Method)) +
  #geom_boxplot()
  geom_violin()+
  ggtitle(title)+theme_gray()
  p
}
pm = plot_res(movie_res,"MovieLens")
pp = plot_res(president_res,"Presidents")
pg = plot_res(gtex_res,"GTEx Z-scores")
pt = plot_res(tumor_res,"Tumors")
pb = plot_res(breast_res,"Breast Cancer")
library(cowplot)
firstrow = plot_grid(pm, pp,pg, labels = c("A","B","C"), ncol = 3,rel_widths = c(1, 1))
secondrow <- plot_grid(pt, pb, labels = c("D","E"), ncol = 2,rel_widths = c(1, 1))
plot_grid(firstrow, secondrow, ncol = 1,rel_widths = c(1, 0.6))

```

@@

there is somethig we don't fully understand. the simplest case is comparing rank 0 and rank 1 case.
